%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Current template author:
% Chia-Chi Hsu
% 
% SIGNIFICANT CHANGES HAVE BEEN MADE TO THE DANA TEMPLATE
% including but not limited to:
% % main font (Lato -> Helvetica)
% % removal of icon definition (\texticon)
% % removal of AWARDS and PUBLICATIONS sections
% % font size of name
% % item gaps (itemsep1pt -> itemsep2pt)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DANA TEMPLATE INFO
% Dana Seidel (danaseidel.com)
% 
% SIGNIFICANT CHANGES HAVE BEEN MADE TO THE ORIGINAL TEMPLATE
% including but not limited to:
% % inclusion of fontawesome icons
% % movement of AWARDS section
% % addition of a short bio and creation of a CONTACT section
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ORIGINAL TEMPLATE INFO
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{deedy-resume}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Chia-Chi Hsu}
{Software Engineer with 3+ years of experience.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.32\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Contact
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Contact}
{\parskip3pt
\href{mailto:devcchsu@gmail.com}{\faEnvelope{ devcchsu@gmail.com}}\vspace{3pt} \\
\href{https://www.linkedin.com/in/devcchsu}{\faLinkedinSquare{ devcchsu}}\vspace{3pt} \\
\href{https://github.com/wuchihsu}{\faGithub{ wuchihsu}}\vspace{3pt} \\
\href{https://goo.gl/maps/CGLqV6QWdAYszMuo9}{\faMapMarker{ Kaohsiung City, Taiwan}}
}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\textbullet{} Golang (Echo, GORM)
\\\textbullet{} Python (NumPy, pandas)
\\\textbullet{} JavaScript (React, dva)
\\\textbullet{} RESTful \textbullet{} WebSocket \textbullet{} gRPC
\\\textbullet{} HLS \textbullet{} WebRTC
\\\textbullet{} Docker (Docker Compose)
\\\textbullet{} Redis \textbullet{} Traefik
\\\textbullet{} Git \textbullet{} GitLab CI/CD
\\\textbullet{} OpenCV \textbullet{} Point Cloud Library
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\subsection{National Tsing Hua University}
\descript{MSc in Electrical Engineering}
\location{2012 - 2014 | Hsinchu City, Taiwan}
Mainly focused on Computer Vision; had experience with C++, OpenCV, Point Cloud Library.
\sectionsep

\subsection{National Tsing Hua University}
\descript{BSc in Electrical Engineering}
\location{2008 - 2012 | Hsinchu City, Taiwan}
Mainly focused on Image Processing; had experience with MATLAB, C++, CUDA C.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience}

\runsubsection{ZIG (startup)}
\descript{| Software Engineer \textbullet{} Internet of Things}
\location{ Jul 2019 - Sept 2020 | Kaohsiung City, Taiwan}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed the backend of a low-latency, plugin-free surveillance web viewer
by requesting Real Time Streaming Protocol (RTSP) streams from a Network Video Recorder (NVR) and transfering H.264 NAL units to the frontend via WebRTC.
\item Created a surveillance video playback service backend using Hikvision NVR's C API to query date information and request Transport Stream (TS) packets,
using cgo to integrate C code into Golang and using HTTP Live Streaming (HLS) to provide streams.
\item Implemented communication protocols (Modbus, YDN23) in Golang to fetch and write data on industrial electronic devices.
\item Built simulated devices for testing and demonstrating our IoT web system.
\item Implemented a Docker web UI that could be easily used by our clients
by using Golang Docker client API for the backend.
\item Created a simple CI/CD pipeline using GitLab CI/CD and kaniko, including Golang code testing, Docker images building and pushing.
\end{tightemize}
\sectionsep

\runsubsection{Wistron}
\descript{| Software Engineer \textbullet{} Computer Vision}
\location{ Dec 2016 - Oct 2018 | Kaohsiung City, Taiwan}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Built a Machine Learning model to classify images of semi-finished products as either OK or NG 
by training a convolutional neural network with data augmentation on thousands images.
\item Developed a simple but effective segmentation process to segment images of semi-finished products into different regions by using Template Matching.
\item Integrated YOLO's pre-trained person detection model into a Person Re-identification system to build an intelligent surveillance system.
\item Built a people counter using Kinect, NVIDIA Jetson TX1 and the open source project OpenPTrack for pedestrian tracking.
\item Wrote and maintained a Dockerfile for Machine Learning model development and deployment.
\item Utilized gRPC to communicate between Python and C\# programs.
\end{tightemize}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Project Experience}

\descript{Quantification of Cranial Asymmetry | Graduate Researcher}
\location{ Oct 2013 - Apr 2014 | Hsinchu City, Taiwan}
\begin{tightemize}
\item Developed a pipeline to align two sets of 3D point clouds for evaluating the treatment of cranial asymmetry in infant
by utilizing Fast Point Feature Histograms (FPFH), Sample Consensus Initial Alignment (SAC-IA) and Iterative Closest Point (ICP).
\end{tightemize}
\sectionsep

\descript{Accelerating Ultrasound Imaging Using CUDA | Technical Support}
\location{ Apr 2012 - Oct 2012 | Hsinchu City, Taiwan}
\begin{tightemize}
\item Reduced signal processing time in Ultrasound imaging by 95\% by using CUDA C modules to calculate Hilbert transform and Delay-and-Sum.
\item Demonstrated CUDA C programing to researchers at Industrial Technology Research Institute.
\end{tightemize}
% \sectionsep

\end{minipage}
\end{document} \documentclass[]{article}